Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-09 chapters/introduction/introduction.tex
changes in background

\subsection{Geo-Calibration}
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually geo-calibration task is
straightforward: given an image, identify the location it was captured
in the world and the direction the camera was facing. Solving this
problem is of great value for a wide variety of fields, with potential
applications ranging from the forensic sciences~\cite{stylianou13jane}
to crowd-sourced environmental monitoring~\cite{zhang2012mining}.

@@

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs have achieved state-of-the-art performances in many computer
vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geolocalization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.  Horizon line is an
important indicator for estimating camera poses.
Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
has been done to to identify the horizon line with CNNs.
Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate
the camera focal length. Kendall \etal~\cite{kendall2015convolutional}
propose a neural network that can identify 6-DOF camera parameters,
but their method only limited to specific scenes.

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an separate section to discuss it. A cross-view image
pair consists of a ground-view image and an overhead image at the
same location. In some cases, two images are also aligned in
orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
extract the overhead features as reference database for
geo-localization.

%Furthermore, there are many other properties of the cross-view pairs
%to explore for high-level feature extraction \todo{expand}.

>>>>

\subsection{Geo-Calibration}
\todo{add deterministic methods, add literature for time estimation}

Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to crowd-sourced environmental
monitoring~\cite{zhang2012mining}.

@@

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.

Closely related to camera geo-calibration, studies also have been done
to identify the camera poses and focal length using deep neural
networks.
Horizon line is an important indicator for estimating camera poses,
which is, giving the focal length, one can derive the camera roll and
pitch angles from the horizon line position in the image.
Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
has been done to to identify the horizon line with CNNs.  Workman
\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
neural network that can identify 6-DOF camera parameters, but their
method only limited to specific scenes.

\subsection{Ground-to-Aerial Geo-Calibration}
Data-driven scene matching approaches are widely used to localize a
query image by registering in a large dataset of geo-tagged images. 
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays, which also makes it a perfect source for
database of geo-tagged. We refer to the geo-calibration process of
matching the ground-level imagery to the aerial imagery as {\em
Ground-to-Aerial Geo-Calibration}.
%
Cross-view image pair is the basic element for ground-to-aerial
geo-calibration. It consists of a ground-level image and an overhead
image at the same location. In some cases, two images are also aligned
in orientation.

\todo{cite ground-to-aerial geo-calibration papers}

### 2018-08-09 chapters/introduction/junk.tex
changes in background

>>>>

Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
%
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
extract the overhead features as reference database for
geo-localization.
